Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-11-17 grove-paper.tex
Add code labels in figure 7 (Editing Nested)
Updates from Overleaf

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureSimple
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{SimpleTimes}{Root}%
\newvertex{SimpleTimes}{*}%
\newedge{SimpleX}{L}%
\newvertex{SimpleX}{x}%
\newcommand{\figureSimple}{
\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.49\linewidth}
\centering
\caption{}
\label{fig:A simple tree with a hole-a}
\includegraphics{code-views/simple.png}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.49\linewidth}
\centering
\caption{}
\label{fig:A simple tree with a hole-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style, color=black] -> {
  "\vSimpleTimes" [> "\eSimpleTimes", >color=black, color=black] -> {
   "\vSimpleX" [> "\eSimpleX"', >color=black, color=black],
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Example of Code that Includes a Hole.
\autoref{fig:A simple tree with a hole-a}:~User Interface for the Code.
\autoref{fig:A simple tree with a hole-b}:~Graph Representation of the Code.}
\label{fig:A simple tree with a hole}
\end{figure}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureMultiChild
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{MultiChildAlice}{R}
\newvertex{MultiChildAlice}{x}
\newedge{MultiChildBob}{R}
\newvertex{MultiChildBob}{y}
\newcommand{\figureMultiChild}{
\begin{figure*}
%\hfill
\hskip0.12\linewidth
%%%%%%%%
\begin{subfigure}[t]{0.21\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (-7.5em,0cm) node (fig-Editing Nested-c-x) [gray,anchor=base west] {{\textbf{\small Fig.~\ref*{fig:Editing Nested-c}}}};
%%%%
\path (0cm,0cm) node (fig-Multi-child conflict-a) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Editing Nested-c-x) to (-2em, 0cm |- fig-Multi-child conflict-a);
\end{tikzpicture}
}
\label{fig:Multi-child-a}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   {
    "\vMultiChildAlice" [> "\eMultiChildAlice", >alice edge, alice node]
   }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.21\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Multi-child conflict-b) [anchor=base] {\strut};
\path [draw,->,bob step] (fig-Editing Nested-c-x) to[out=15,in=165] (-2em, 0cm |- fig-Multi-child conflict-b);
\end{tikzpicture}
}
\label{fig:Multi-child-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   "\vMultiChildBob" [> "\eMultiChildBob", >bob edge, bob node]
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.21\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Multi-child conflict-c) [anchor=base] {\strut};
\path [draw,->,merge step] (fig-Multi-child conflict-a) to[out=15,in=165] (-2em, 0cm |- fig-Multi-child conflict-c);
\path [draw,->,merge step] (fig-Multi-child conflict-b) to (-2em, 0cm |- fig-Multi-child conflict-c);
\end{tikzpicture}
}
\label{fig:Multi-child-c}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'anchor=-15] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   "\vMultiChildAlice" [> "\eMultiChildAlice"anchor=153, >merge edge, merge node],
   {},
   "\vMultiChildBob" [> "\eMultiChildBob"anchor=195, >merge edge, merge node]
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.21\linewidth}
\centering
\caption{}
\label{fig:Multi-child-d}
\includegraphics{code-views/multi-child-conflict.png}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Example of Multi-Child Conflicts.}
\label{fig:Multi-child}
\end{figure*}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureMultiParent
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{MultiParentAlice}{R}
\newedge{MultiParentBob}{R}
\newcommand{\figureMultiParent}{
\begin{figure*}
%\hfill
\hskip0.12\linewidth
%%%%%%%%
\begin{subfigure}[t]{0.14\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (-7.5em,0cm) node (fig-Multi-child-c-x) [gray,anchor=base west] {{\textbf{\small Fig.~\ref*{fig:Multi-child-c}}}};
%%%%
\path (0cm,0cm) node (fig-Multi-parent-a) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Multi-child-c-x) to[star] (-2em, 0cm |- fig-Multi-parent-a);
\end{tikzpicture}
}
\label{fig:Multi-parent-a}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    {}
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.14\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Multi-parent-b) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Multi-parent-a) to[star] (-2em, 0cm |- fig-Multi-parent-b);
\end{tikzpicture}
}
\label{fig:Multi-parent-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    {},
    "\vNestedAlice" [> "\eMultiParentAlice"', >alice edge]
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.14\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Multi-parent-c) [anchor=base] {\strut};
\path [draw,->,bob step] (fig-Multi-parent-a) to[out=15,in=165,star] (-2em, 0cm |- fig-Multi-parent-c);
\end{tikzpicture}
}
\label{fig:Multi-parent-c}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'],
   "\vNestedAlice" [> "\eMultiParentBob", >bob edge]
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.14\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Multi-parent-d) [anchor=base] {\strut};
\path [draw,->,merge step] (fig-Multi-parent-b) to[out=15,in=165] (-2em, 0cm |- fig-Multi-parent-d);
\path [draw,->,merge step] (fig-Multi-parent-c) to[out=15,in=165] (-2em, 0cm |- fig-Multi-parent-d);
\end{tikzpicture}
}
\label{fig:Multi-parent-d}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  a/{\vWrapPlus} [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    {},
    b/"\vNestedAlice" [> "\eMultiParentAlice"', >merge edge]
   },
   {}
  }
 },
};
\path [draw,->,merge edge] (a) to ["\eMultiParentBob",out=-60,in=60] (b);
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.14\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Multi-parent-e) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Multi-parent-d) to (-2em, 0cm |- fig-Multi-parent-e);
\end{tikzpicture}
}
\label{fig:Multi-parent-e}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  v8/"\vWrapPlus" [> "\eWrapPlus"] -> {
   v2/"\vSimpleTimes" [> "\eNestedBob"'] -> {
    {},
    "\vNestedAlice" [> "\eMultiParentAlice"']
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.14\linewidth}
\centering
\caption{}
\label{fig:Multi-parent-f}
\includegraphics{code-views/multi-parent-conflict.png}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Example of Multi-Parent Conflicts.}
\label{fig:Multi-parent}
\end{figure*}
}

@@

\includegraphics{code-views/cycle.png}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureDisconnection
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{DisconnectionAlice}{R}
\newedge{DisconnectionBob}{L}
\newcommand{\figureDisconnection}{
\begin{figure*}
%\hfill
\hskip0.12\linewidth
%%%%%%%%
\begin{subfigure}[t]{0.17\textwidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (-7.5em,0cm) node (fig-Multi-User Cycles-d-x) [gray,anchor=base west] {{\textbf{\small Fig.~\ref*{fig:Multi-User Cycles-d}}}};
%%%%
\path (0cm,0cm) node (fig-Disconnection-a) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Multi-User Cycles-d-x) to[star] (-2em, 0cm |- fig-Disconnection-a);
\end{tikzpicture}
}
\label{fig:Disconnection-a}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'],
   "\vMultiCycleTimes" [> "\eMultiCycleAliceTimes"]
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.17\textwidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Disconnection-b) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Disconnection-a) to[star] (-2em, 0cm |- fig-Disconnection-b);
\end{tikzpicture}
}
\label{fig:Disconnection-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    {},
    "\vMultiCycleTimes" [> "\eDisconnectionAlice", >alice edge]
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.17\textwidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Disconnection-c) [anchor=base] {\strut};
\path [draw,->,bob step] (fig-Disconnection-a) to[out=15,in=165,star] (-2em, 0cm |- fig-Disconnection-c);
\end{tikzpicture}
}
\label{fig:Disconnection-c}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vMultiCycleTimes" [> "\eMultiCycleAliceTimes"] -> {
    "\vSimpleTimes" [> "\eDisconnectionBob"', >bob edge],
    {}
   }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.17\textwidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Disconnection-d) [anchor=base] {\strut};
\path [draw,->,merge step] (fig-Disconnection-b) to[out=15,in=165] (-2em, 0cm |- fig-Disconnection-d);
\path [draw,->,merge step] (fig-Disconnection-c) to (-2em, 0cm |- fig-Disconnection-d);
\end{tikzpicture}
}
\label{fig:Disconnection-d}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"]
 }
};
\path (-0.5cm,-2cm) graph[graph style] { plus/"\vSimpleTimes" };
\path ( 0.5cm,-2cm) graph[graph style] { times/"\vMultiCycleTimes" };
\path[draw,->,merge edge] (times) to ["\eMultiCycleBobTimes"'anchor=north,out=-135,in=-45] (plus);
\path[draw,->,merge edge] (plus) to ["\eMultiCycleBobPlus"anchor=south,out=45,in=135] (times);
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.17\linewidth}
\centering
\caption{}
\label{fig:Disconnection-e}
\includegraphics{code-views/disconnected-reachable.png}
\includegraphics{code-views/disconnected-unreachable.png}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Example of Disconnection.}
\label{fig:Disconnection}
\end{figure*}
}

@@

\author{Eric Griffis}
\orcid{0000-0003-1693-6172}

@@

Alice adds~\vDifferentAlice{} as the left child of \vSimpleTimes{}
and Bob changes \vConstructionY{} to \vDifferentBob{}.
Before transmitting their edits to each other,
Alice and Bob have the graphs in \autoref{fig:Editing Different Parts of the Code-a}
and \autoref{fig:Editing Different Parts of the Code-b}, respectively.
(Note that thee transition edge from \autoref{fig:Move-b} to
\autoref{fig:Editing Different Parts of the Code-b} represents
multiple edges (i.e., deleting~\eConstructionY{} and adding~\eDifferentBob{} along with its child~\vDifferentBob{}).
We thus mark it with a star.)\todo{star size}\todo{"sync"}

@@

@@

The language we are modeling is shown in \autoref{fig:Syntax as a grammar},
standard for a simply-typed lambda calculus except that all types of terms have
holes (represented by $\hole$). In particular, the argument to a lambda can be
either a bound variable or a hole.

% In order to model this we define

% Turn that into a constructor set K + position set P + arity function (has type: K -> $\wp$(P)).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureSimple
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{SimpleTimes}{Root}%
\newvertex{SimpleTimes}{*}%
\newedge{SimpleX}{L}%
\newvertex{SimpleX}{x}%
\newcommand{\figureSimple}{
\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.49\linewidth}
\centering
\caption{}
\label{fig:A simple tree with a hole-a}
TODO
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.49\linewidth}
\centering
\caption{}
\label{fig:A simple tree with a hole-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style, color=black] -> {
  "\vSimpleTimes" [> "\eSimpleTimes", >color=black, color=black] -> {
   "\vSimpleX" [> "\eSimpleX"', >color=black, color=black],
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Example of Code that Includes a Hole.
\autoref{fig:A simple tree with a hole-a}:~User Interface for the Code.
\autoref{fig:A simple tree with a hole-b}:~Graph Representation of the Code.}
\label{fig:A simple tree with a hole}
\end{figure}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureMultiChild
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{MultiChildAlice}{R}
\newvertex{MultiChildAlice}{x}
\newedge{MultiChildBob}{R}
\newvertex{MultiChildBob}{y}
\newcommand{\figureMultiChild}{
\begin{figure*}
%\hfill
\hskip0.12\linewidth
%%%%%%%%
\begin{subfigure}[t]{0.21\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (-7.5em,0cm) node (fig-Editing Nested-c-x) [gray,anchor=base west] {{\textbf{\small Fig.~\ref*{fig:Editing Nested-c}}}};
%%%%
\path (0cm,0cm) node (fig-Multi-child conflict-a) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Editing Nested-c-x) to (-2em, 0cm |- fig-Multi-child conflict-a);
\end{tikzpicture}
}
\label{fig:Multi-child-a}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   {
    "\vMultiChildAlice" [> "\eMultiChildAlice", >alice edge, alice node]
   }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.21\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Multi-child conflict-b) [anchor=base] {\strut};
\path [draw,->,bob step] (fig-Editing Nested-c-x) to[out=15,in=165] (-2em, 0cm |- fig-Multi-child conflict-b);
\end{tikzpicture}
}
\label{fig:Multi-child-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   "\vMultiChildBob" [> "\eMultiChildBob", >bob edge, bob node]
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.21\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Multi-child conflict-c) [anchor=base] {\strut};
\path [draw,->,merge step] (fig-Multi-child conflict-a) to[out=15,in=165] (-2em, 0cm |- fig-Multi-child conflict-c);
\path [draw,->,merge step] (fig-Multi-child conflict-b) to (-2em, 0cm |- fig-Multi-child conflict-c);
\end{tikzpicture}
}
\label{fig:Multi-child-c}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'anchor=-15] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    "\vDifferentBob" [> "\eDifferentBob"]
   },
   "\vMultiChildAlice" [> "\eMultiChildAlice"anchor=153, >merge edge, merge node],
   {},
   "\vMultiChildBob" [> "\eMultiChildBob"anchor=195, >merge edge, merge node]
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.21\linewidth}
\centering
\caption{}
\label{fig:Multi-child-d}
TODO: show UI
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Example of Multi-Child Conflicts.}
\label{fig:Multi-child}
\end{figure*}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureMultiParent
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{MultiParentAlice}{R}
\newedge{MultiParentBob}{R}
\newcommand{\figureMultiParent}{
\begin{figure*}
%\hfill
\hskip0.12\linewidth
%%%%%%%%
\begin{subfigure}[t]{0.14\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (-7.5em,0cm) node (fig-Multi-child-c-x) [gray,anchor=base west] {{\textbf{\small Fig.~\ref*{fig:Multi-child-c}}}};
%%%%
\path (0cm,0cm) node (fig-Multi-parent-a) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Multi-child-c-x) to[star] (-2em, 0cm |- fig-Multi-parent-a);
\end{tikzpicture}
}
\label{fig:Multi-parent-a}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    "\vNestedAlice" [> "\eNestedAlice"'],
    {}
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.14\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Multi-parent-b) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Multi-parent-a) to[star] (-2em, 0cm |- fig-Multi-parent-b);
\end{tikzpicture}
}
\label{fig:Multi-parent-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    {},
    "\vNestedAlice" [> "\eMultiParentAlice"', >alice edge]
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.14\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Multi-parent-c) [anchor=base] {\strut};
\path [draw,->,bob step] (fig-Multi-parent-a) to[out=15,in=165,star] (-2em, 0cm |- fig-Multi-parent-c);
\end{tikzpicture}
}
\label{fig:Multi-parent-c}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'],
   "\vNestedAlice" [> "\eMultiParentBob", >bob edge]
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.14\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Multi-parent-d) [anchor=base] {\strut};
\path [draw,->,merge step] (fig-Multi-parent-b) to[out=15,in=165] (-2em, 0cm |- fig-Multi-parent-d);
\path [draw,->,merge step] (fig-Multi-parent-c) to[out=15,in=165] (-2em, 0cm |- fig-Multi-parent-d);
\end{tikzpicture}
}
\label{fig:Multi-parent-d}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  a/{\vWrapPlus} [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    {},
    b/"\vNestedAlice" [> "\eMultiParentAlice"', >merge edge]
   },
   {}
  }
 },
};
\path [draw,->,merge edge] (a) to ["\eMultiParentBob",out=-60,in=60] (b);
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.14\linewidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Multi-parent-e) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Multi-parent-d) to (-2em, 0cm |- fig-Multi-parent-e);
\end{tikzpicture}
}
\label{fig:Multi-parent-e}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  v8/"\vWrapPlus" [> "\eWrapPlus"] -> {
   v2/"\vSimpleTimes" [> "\eNestedBob"'] -> {
    {},
    "\vNestedAlice" [> "\eMultiParentAlice"']
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.14\linewidth}
\centering
\caption{}
\label{fig:Multi-parent-f}
TODO: UI
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Example of Multi-Parent Conflicts.}
\label{fig:Multi-parent}
\end{figure*}
}

@@

TODO: UI

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \figureDisconnection
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newedge{DisconnectionAlice}{R}
\newedge{DisconnectionBob}{L}
\newcommand{\figureDisconnection}{
\begin{figure*}
%\hfill
\hskip0.12\linewidth
%%%%%%%%
\begin{subfigure}[t]{0.17\textwidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (-7.5em,0cm) node (fig-Multi-User Cycles-d-x) [gray,anchor=base west] {{\textbf{\small Fig.~\ref*{fig:Multi-User Cycles-d}}}};
%%%%
\path (0cm,0cm) node (fig-Disconnection-a) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Multi-User Cycles-d-x) to[star] (-2em, 0cm |- fig-Disconnection-a);
\end{tikzpicture}
}
\label{fig:Disconnection-a}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'],
   "\vMultiCycleTimes" [> "\eMultiCycleAliceTimes"]
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.17\textwidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Disconnection-b) [anchor=base] {\strut};
\path [draw,->,alice step] (fig-Disconnection-a) to[star] (-2em, 0cm |- fig-Disconnection-b);
\end{tikzpicture}
}
\label{fig:Disconnection-b}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   "\vSimpleTimes" [> "\eNestedBob"'] -> {
    {},
    "\vMultiCycleTimes" [> "\eDisconnectionAlice", >alice edge]
   },
   {}
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.17\textwidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Disconnection-c) [anchor=base] {\strut};
\path [draw,->,bob step] (fig-Disconnection-a) to[out=15,in=165,star] (-2em, 0cm |- fig-Disconnection-c);
\end{tikzpicture}
}
\label{fig:Disconnection-c}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"] -> {
   {},
   "\vMultiCycleTimes" [> "\eMultiCycleAliceTimes"] -> {
    "\vSimpleTimes" [> "\eDisconnectionBob"', >bob edge],
    {}
   }
  }
 }
};
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.17\textwidth}
\centering
\caption{
\begin{tikzpicture}[remember picture, overlay]
\path (0cm,0cm) node (fig-Disconnection-d) [anchor=base] {\strut};
\path [draw,->,merge step] (fig-Disconnection-b) to[out=15,in=165] (-2em, 0cm |- fig-Disconnection-d);
\path [draw,->,merge step] (fig-Disconnection-c) to (-2em, 0cm |- fig-Disconnection-d);
\end{tikzpicture}
}
\label{fig:Disconnection-d}
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "\vWrapPlus" [> "\eWrapPlus"]
 }
};
\path (-0.5cm,-2cm) graph[graph style] { plus/"\vSimpleTimes" };
\path ( 0.5cm,-2cm) graph[graph style] { times/"\vMultiCycleTimes" };
\path[draw,->,merge edge] (times) to ["\eMultiCycleBobTimes"'anchor=north,out=-135,in=-45] (plus);
\path[draw,->,merge edge] (plus) to ["\eMultiCycleBobPlus"anchor=south,out=45,in=135] (times);
\end{tikzpicture}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}[t]{0.17\linewidth}
\centering
\caption{}
\label{fig:Disconnection-e}
TODO: UI
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Example of Disconnection.}
\label{fig:Disconnection}
\end{figure*}
}

@@

\author{Eric Griffis}
\orcid{nnnn-nnnn-nnnn-nnnn}

@@

Alice adds~\vDifferentAlice{} as the left child of \vSimpleTimes{}
and Bob changes \vConstructionY{} to \vDifferentBob{}.
Before transmitting their edits to each other,
Alice and Bob have the graphs in \autoref{fig:Editing Different Parts of the Code-a}
and \autoref{fig:Editing Different Parts of the Code-b}, respectively.
(Note that thee transition edge from \autoref{fig:Move-b} to
\autoref{fig:Editing Different Parts of the Code-b} represents
multiple edges (i.e., deleting~\eConstructionY{} and adding~\eDifferentBob{} along with its child~\vDifferentBob{}).
We thus mark it with a star.)

@@

Like Hazel, cursor position are a position in the tree, not a particular character.
They wrap around an expression

In most cases, cursor on position.  This has the advantage of remaining stable
if the other user deletes the code under the cursor.
However, when there are multiple children, cursors need to be specific
to a particular edge.

@@

The language we are modeling is shown in \autoref{fig:Syntax as a grammar}.
Standard for a simply-typed lambda calculus except that
all terms have holes (represented by $\_$)
and the argument to a lambda is its own term.
The latter of which allows us to express lambdas with a hole for the bound variable.

In order to model this we define

Turn that into a constructor set K + index set I + arity function (has type: K -> $\wp$(I)).

\begin{figure}
\[
\arraycolsep=0pt
\begin{array}{ll}
 \arity : \K \rightarrow & \wp(\I) \\
 \hline
 \arity(\Root)={}     & \left\{ \Root \right\} \\
 \arity(\PatVar)={}   & \left\{ \right\} \\
 \arity(\ExpVar)={}   & \left\{ \right\} \\
 \arity(\ExpLam)={}   & \left\{ \LamParam, \LamType, \LamBody \right\} \\
 \arity(\ExpApp)={}   & \left\{ \AppFun, \AppArg \right\} \\
 \arity(\ExpPlus)={}  & \left\{ \PlusLeft, \PlusRight \right\} \\
 \arity(\TypArrow)={} & \left\{ \ArrowArg, \ArrowResult \right\} \\
 \arity(\TypNum)={}   & \left\{ \right\} \\
\end{array}
\]
\caption{Constructors, Indexes and Arity}
\label{fig:Constructors, Indexes and Arity}
\end{figure}
